Compiling a corpus into an LLM-written, self-maintaining wiki --- rather than retrieving from raw chunks at query time --- has been proposed as a replacement for RAG on evolving corpora \citep{karpathy2026wiki}. We study what such a compiled store needs beyond a good initial compile: a way to know it is still current, a way to update it without silently destroying what it already knows, and a way to remove something from it that must go. We present empirical evidence for a four-stage lifecycle --- \emph{compile, certify, maintain, retract} --- validated across real third-party systems (LightRAG, RAPTOR, a faithfully-reproduced third-party LLM-Wiki update policy) and two datasets (HoH, SciFact-Open). Compiling with recency-aware supersession resolution nearly eliminates staleness error (SER $0.007$ vs.\ $0.277$--$0.280$ for vector-RAG and graph-RAG baselines, $n{=}300$); a controlled dissociation shows the operative variable is resolution, not memory or graph structure. A finite-sample $(\delta,\varepsilon)$ contract, corrected for noisy LLM judges, certifies fidelity and currency under incremental maintenance at $40$--$47\%$ of full-audit cost, and exposes two failure modes worth naming: a \emph{build lottery} where nominally identical compiles disagree on $17$--$23\%$ of claims, and an \emph{adaptivity trap} where self-audited repair overclaims true retention by $52$ points. A minimal offline-trained maintainer beats the best prompted maintainer at equal deploy cost ($+0.127$ retention, $p{=}0.009$) without being reward-gameable at slack budgets, and a per-batch anytime-valid retention bound (LossGate) wraps any maintainer with a certified floor that rejects harmful updates, lifting retention by $0.12$--$0.14$ over the same maintainer ungated. Finally, we show that retracting a fact from an agent's memory does not make it stay retracted: a correctness-gated deletion leaves $99.0\%$ of retracted facts recoverable through the agent's own memory-consolidation loop --- statistically indistinguishable from no deletion at all --- while a cheap, weight-free membership-keyed veto reduces recoverability to $0.0\%$, matching a never-ingested oracle. We report every result with the seed count, statistical test, and scope it actually has, and we are explicit about what is not yet established: single-build variance in the compile stage, an untested half of a maintenance boundary law, and an open problem in formally certifying retraction of claims fused across multiple sources. Code, data pointers, and a reproduction guide for every stage accompany this paper.
