\section{Limitations}
\label{sec:limitations}

We list every limitation identified during the writing of this paper, organized by stage, rather than folding them into a single generic paragraph. This paper has not been externally peer-reviewed; the items below are what our own scrutiny of each result surfaced.

\textbf{Compile (\S\ref{sec:compile}).} The HoH result is a single build and a single run: no seed variance is reported for the compile step itself, so we cannot separate genuine effect size from build-to-build noise at the level \S\ref{sec:build-lottery} shows exists for the compiler in general. The scaled substrate is HoH-only; a second substrate (source code libraries) is a small consistent check ($n{=}14/13$), not a powered second benchmark. A static-audit cross-pipeline probe using a different reader, embedder, and substrate (SciFact-Open) is directional, not a controlled comparison, because the intended matched-pipeline version could not be run (a shared-GPU thread-limit conflict with other jobs on the host). The external-validation experiment (\S\ref{sec:compile-external}) is single-seed and self-judged by the same model that performed the rewrite, at temperature $0$; an independent, calibrated judge pass for that specific experiment has not been run.

\textbf{Certify (\S\ref{sec:certify}).} The compiler/judge model family is varied (Qwen vs.\ Llama) only for the fidelity gate experiment; every other certified number in this section uses Qwen for both compiler and judge, so cross-family generality of the maintained-certificate and adaptivity-trap results specifically is untested. Judge-noise calibration uses a constructed present/absent pair set, not human-labeled data. The dense-RAG comparator uses oracle page routing, isolating page-content fidelity from retrieval-routing error --- a real deployed RAG system would also incur routing loss that this comparison does not charge it for.

\textbf{Maintain (\S\ref{sec:maintain}).} The single largest open risk in this paper: the boundary law's dangerous regime (an RL-trained maintainer, or a maintainer facing a fixed and predictable audit schedule, where gaming the audit signal is the direct training objective rather than a side effect of offline selection) has not been run, only predicted by extrapolation from the offline-selection regime. The binding-budget policy difference-in-differences ($+0.022$) is below its own estimated noise floor, so the $\sim\!6\times$ signal-laundering ratio should be read as directional, not precise. A second model scale was not run, for a disclosed reason (avoiding GPU contention with others' concurrent jobs), not because it was attempted and failed. The LoRA-wrapped LossGate arm and the rollback-threshold sweep are each single-seed.

\textbf{Retract (\S\ref{sec:retract}).} The primary $n{=}250$ ladder result uses one composition template and one primary model (Qwen3-14B); the second-model probe (Llama) is $n{=}24$ with a noisy no-op control and tests a different memory architecture's block-plus-archival substrate rather than a matched second run of the same experiment. We do not consider ``two substrates plus a directional probe'' equivalent to ``validated across two model families,'' and say so explicitly rather than letting the stronger-sounding framing stand. The complementary serving-time leakage-refusal result has a small correct-and-retracted stratum ($n{=}15$) and shares a model family between backbone and judge. Formally certifying retraction of a claim whose content is fused across multiple sources is, as stated in \S\ref{sec:retract}, an open problem this paper does not solve --- we considered a formal residue-metric criterion for this case and found it structurally unsound (\S\ref{sec:retract}), so we do not carry it forward as a claim, rather than present a contested result as settled.

\textbf{Cross-cutting.} Every stage's headline experiments were run under a shared-GPU, non-disruptive-use policy that occasionally forced a scale-up or a second run to be skipped rather than delayed indefinitely; we have tried to flag every instance where this affected a specific result rather than only mentioning the policy once here. No stage in this paper has had a genuinely external (non-author) peer review pass; the checks we ran ourselves are what shaped which results are reported and how.
