\section{Related work}
\label{sec:related}

\paragraph{Compiled knowledge stores.} The LLM-Wiki pattern we study originates with \citet{karpathy2026wiki}. Closest prior work on certifying compiled stores is \citet{wicer} (iterative wiki-memory compile-evaluate-refine) and \citet{streaming} (proactive materiality-scored pinning for time-evolving compiled stores), neither of which ships a statistical certificate of the kind in \S\ref{sec:certify}; \citet{cochran2026wikirag} independently benchmark vector RAG against an LLM-compiled wiki on a smaller multi-domain corpus, consistent in direction with \S\ref{sec:compile} but without the structure-vs-resolution dissociation. Graph- and tree-structured RAG systems --- LightRAG \citep{guo2025lightrag} and RAPTOR \citep{sarthi2024raptor} --- are the real accumulating-structured baselines we compare against directly rather than re-implement.

\paragraph{Conformal and finite-sample certification.} Our $(\delta,\varepsilon)$ contract follows the general conformal-prediction and PAC-style finite-sample certification tradition, most directly \citet{conformal}'s conformal importance guarantees for summarization; \citet{schuirmann1987tost}'s two one-sided tests procedure underlies the equivalence claim in \S\ref{sec:retract}. Sequential and anytime-valid inference --- the confidence-sequence structure LossGate's stream bound uses --- follows the betting/e-process line of work on bounded-random-variable estimation.

\paragraph{Model editing and knowledge maintenance.} Localized parameter editing \citep{meng2022rome,meng2023memit} and surveys thereof \citep{yao2023editing} address a related but distinct problem: updating a model's weights rather than a compiled text store. \citet{gupta2024editing} document catastrophic forgetting under repeated large-scale edits, a weight-space analogue of the rewrite-damage phenomenon we measure in text stores (\S\ref{sec:compile}, \S\ref{sec:maintain}); \citet{lyaplock2025} study bounded knowledge preservation in sequential editing with a Lyapunov-style stability argument, complementary to our empirical per-batch bound. Retrieval-side dynamic-corpus benchmarks include \citet{liska2022streamingqa} and the HoH benchmark \citep{ouyang2025hoh} we build on directly.

\paragraph{Model and retrieval collapse.} \citet{shumailov2024collapse} and \citet{gerstgrasser2024collapse} study collapse under recursive training on model-generated data; \citet{modelcollapse2025} and \citet{retrievalcollapse} extend this to knowledge fidelity and retrieval quality specifically under recursive synthetic pollution. Our compile- and maintenance-stage decay results are a related but distinct phenomenon --- information loss under repeated \emph{editorial rewriting} of a fixed underlying fact set, not training-distribution collapse from synthetic data --- but the failure mode (fluent output, silently wrong or missing content) rhymes closely enough that we treat this as the closest adjacent literature.

\paragraph{Machine unlearning and retraction.} Benchmark-style unlearning work \citep{maini2024tofu,shi2024muse,jin2024rwku,chen2024flat} and the broader unlearning survey \citep{bourtoule2021machine} target weight-level forgetting, evaluated by whether a model's output distribution changes; \citet{eldan2023whosharrypotter} and \citet{ye2024harrypotterleak} probe residual leakage after unlearning specifically. \citet{pawelczyk2024incontext} study in-context (prompt-level, not weight-level) unlearning. \citet{agenticunlearning2026} is the closest prior work to \S\ref{sec:retract}'s setting --- unlearning inside an LLM-agent memory loop rather than a static model --- though it does not identify or measure the backflow phenomenon via autonomous consolidation that is this section's central finding. \citet{liu2024unlearnrag} study unlearning for RAG systems specifically, a serving-time-retrieval analogue of the write-time retraction problem we study. Deletion under database-style privacy guarantees \citep{inference2026deletion} and cognitive-memory-architecture forgetting benchmarks \citep{forgetful2026} are adjacent settings without the agent-consolidation mechanism central to backflow.

\paragraph{Agent memory systems.} Mem0 \citep{chhikara2025mem0} and MemGPT/Letta \citep{packer2023memgpt} are the two agent-memory architectures we test the membership-veto mechanism against as the primary and secondary substrates in \S\ref{sec:retract}, unmodified except for the write-hook gate we add.
